Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium revision (\YellowPaperVersionNumber{})}}

### 2018-01-23 Paper.tex
hypertargets lines 871–882 exec params

The final state, $\boldsymbol{\sigma}'$, is reached after deleting all accounts that either appear in the self-destruct list or are touched and empty:
\begin{eqnarray}
\boldsymbol{\sigma}' & \equiv & \boldsymbol{\sigma}^* \quad \text{except} \hypertarget{self_destruct_list_A__s}{self_destruct_list_A__s}\\
\forall i \in A_\mathbf{s}: \boldsymbol{\sigma}'[i] & = & \varnothing \hypertarget{touched_A__t}{touched_A__t}\\
\forall i \in A_\mathbf{t}: \boldsymbol{\sigma}'[i] & = & \varnothing \quad\text{if}\quad \mathtt{\tiny DEAD}(\boldsymbol{\sigma}^*\kern -2pt, i)
\end{eqnarray}

\hypertarget{tx_total_gas_used_Upsilon_pow_g}{tx_total_gas_used_Upsilon_pow_g}\hypertarget{tx_logs_Upsilon_pow_l}{tx_logs_Upsilon_pow_l}\hypertarget{tx_status_Upsilon_pow_s}
And finally, we specify $\Upsilon^g$, the total gas used in this transaction, $\Upsilon^\mathbf{l}$, the logs created by this transaction and $\Upsilon^{s}$, the status code of this transaction:
\begin{eqnarray}
\Upsilon^g(\boldsymbol{\sigma}, T) & \equiv & T_g - g' \\
\Upsilon^\mathbf{l}(\boldsymbol{\sigma}, T) & \equiv & A_\mathbf{l} \\
\Upsilon^s(\boldsymbol{\sigma}, T) & \equiv & s'
\end{eqnarray}

@@

\section{Contract Creation} \label{ch:create}
\hypertarget{endow}{endow}

@@

\begin{itemize}
\item $I_a$, the address of the account which owns the code that is executing.
\item $I_o$, the sender address of the transaction that originated this execution.
\item $I_p$, the price of gas in the transaction that originated this execution.
\item $I_\mathbf{d}$, the byte array that is the input data to this execution; if the execution agent is a transaction, this would be the transaction data.
\item $I_s$, the address of the account which caused the code to be executing; if the execution agent is a transaction, this would be the transaction sender.
\item $I_v$, the value, in Wei, passed to this account as part of the same procedure as execution; if the execution agent is a transaction, this would be the transaction value.
\item $I_\mathbf{b}$, the byte array that is the machine code to be executed.
\item $I_H$, the block header of the present block.
\item $I_e$, the depth of the present message-call or contract-creation (i.e. the number of {\small CALL}s or {\small CREATE}s being executed at present).
\item $I_w$, the permission to make modifications to the state.
\end{itemize}

>>>>

The final state, $\boldsymbol{\sigma}'$, is reached after deleting all accounts that either appear in the self-destruct list or are touched and empty:
\begin{eqnarray}
\boldsymbol{\sigma}' & \equiv & \boldsymbol{\sigma}^* \quad \text{except} \\
\forall i \in A_\mathbf{s}: \boldsymbol{\sigma}'[i] & = & \varnothing \\
\forall i \in A_\mathbf{t}: \boldsymbol{\sigma}'[i] & = & \varnothing \quad\text{if}\quad \mathtt{\tiny DEAD}(\boldsymbol{\sigma}^*\kern -2pt, i)
\end{eqnarray}

And finally, we specify $\Upsilon^g$, the total gas used in this transaction, $\Upsilon^\mathbf{l}$, the logs created by this transaction and $\Upsilon^{s}$, the status code of this transaction:
\begin{eqnarray}
\Upsilon^g(\boldsymbol{\sigma}, T) & \equiv & T_g - g' \\
\Upsilon^\mathbf{l}(\boldsymbol{\sigma}, T) & \equiv & A_\mathbf{l} \\
\Upsilon^s(\boldsymbol{\sigma}, T) & \equiv & s'
\end{eqnarray}

@@

\section{Contract Creation} \label{ch:create}

@@

\begin{itemize}\hypertarget{address_of_account_which_owns_code_I__a_def_words}{address_of_account_which_owns_code_I__a_def_words}
\item $I_a$, the address of the account which owns the code that is executing.\hypertarget{address_of_sender_of_tx_that_originated_execution_I__o}{address_of_sender_of_tx_that_originated_execution_I__o}
\item $I_o$, the sender address of the transaction that originated this execution.\hypertarget{gas_price_in_tx_that_originated_execution_I__p}{gas_price_in_tx_that_originated_execution_I__p}
\item $I_p$, the price of gas in the transaction that originated this execution.\hypertarget{execution_input_data_I__d}{execution_input_data_I__d}
\item $I_\mathbf{d}$, the byte array that is the input data to this execution; if the execution agent is a transaction, this would be the transaction data.\hypertarget{the_address_of_the_account_which_caused_the_code_to_be_executing_I__s}{the_address_of_the_account_which_caused_the_code_to_be_executing_I__s}
\item $I_s$, the address of the account which caused the code to be executing; if the execution agent is a transaction, this would be the transaction sender.\hypertarget{Wei_value_exec}{Wei_value_exec_I__v}
\item $I_v$, the value, in Wei, passed to this account as part of the same procedure as execution; if the execution agent is a transaction, this would be the transaction value.\hypertarget{exec_machine_code_I__b}{exec_machine_code_I__b}
\item $I_\mathbf{b}$, the byte array that is the machine code to be executed.\hypertarget{exec_block_header_I__H}{exec_block_header_I__H}
\item $I_H$, the block header of the present block.\hypertarget{exec_call_or_create_depth_I__e}{exec_call_or_create_depth_I__e}
\item $I_e$, the depth of the present message-call or contract-creation (i.e. the number of {\small CALL}s or {\small CREATE}s being executed at present).\hypertarget{exec_permission_to_modify_state_I__w}{exec_permission_to_modify_state_I__w}
\item $I_w$, the permission to make modifications to the state.
\end{itemize}
